
\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.6cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

\setlist[itemize]{noitemsep, topsep=2pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
{\LARGE \textbf{Rundong Zhou}} \\[-2pt]
London, United Kingdom \\[-2pt]
{ab945669519@gmail.com} \,|\, +44 7442 380329 \\[-2pt]
{linkedin.com/in/rundong-zhou-aa97251b6}\\[-2pt]
{https://github.com/sheeshpanda15}
\end{center}

\vspace{0.3cm}

\section*{Profile}
PhD candidate in Statistics at King’s College London with a strong foundation in mathematical statistics,
data modelling, and applied data analysis. Experienced in academic teaching and quantitative problem-solving,
with strong programming skills and a solid understanding of modern machine learning and large-scale data algorithms.

\section*{Education}

\quad \textbf{King’s College London} \\
PhD in Statistics \hfill Feb 2024 -- Feb 2028 (expected)
\begin{itemize}
\item Led rigorous research initiatives focused on advanced statistical modelling, data science, and the development of application-oriented statistical methods, directly supporting data-driven decision-making.
\item Possess advanced training in mathematical statistics and comprehensive quantitative analysis, providing a strong foundation for sophisticated data interpretations and model development.
\end{itemize}

\textbf{King’s College London} \\
MSc in Complex system modelling \hfill Sep 2022 -- Aug 2023
\begin{itemize}
\item Proficient in end-to-end data analysis, robust data modelling, and the application of diverse statistical methods, complemented by a solid understanding of database systems for efficient data management.
\item Leveraged extensive technical proficiency in Python, R, and Excel for advanced data processing, statistical modelling, and generating actionable insights from complex datasets.
\end{itemize}

\textbf{University of Reading} \\
BSc in Mathematics and Applied Mathematics (First Class Honours) \hfill Sep 2018 -- Jun 2022

\section*{Academic \& Teaching Experience}
\quad \textbf{Clustered Grouping Orthogonal Subsampling} \\
\begin{itemize}
\item Independently developed an innovative subsampling method specifically designed for unlabelled big datasets, demonstrating a proactive approach to solving complex data challenges and enhancing data efficiency and model performance.
\item Achieved a superior performance, demonstrating at least a 20\% reduction in Mean Squared Error (MSE) for parameter estimation compared to existing methods across the estimated dataset, highlighting significant quantitative model optimization.
\item Further enhanced model accuracy, achieving at least a 40\% improvement in Mean Squared Error (MSE) for parameter estimation over alternative approaches, showcasing exceptional analytical and optimization capabilities.
\end{itemize}
\quad \textbf{Graduate Teaching Assistant (GTA)} \\
King’s College London \hfill Sep 2024 -- Present
\begin{itemize}
\item Effectively communicated complex quantitative concepts by delivering tutorials in mathematics, statistics, and data science, fostering understanding and skill development among students.
\item Provided comprehensive support to undergraduate students, guiding them through challenging coursework and enhancing their quantitative problem-solving abilities.
\end{itemize}

\textbf{Undergraduate Teaching Assistant} \\
University of Reading \hfill Jun 2020 -- Jun 2022
\begin{itemize}
\item Actively contributed to the delivery of undergraduate mathematics modules, assisting in teaching and reinforcing fundamental quantitative principles.
\item Offered personalized one-to-one academic and tutorial support, effectively addressing individual learning needs and facilitating deeper comprehension of complex subjects.
\end{itemize}

\section*{Invited Talk}

\textbf{CFE--CMStatistics 2025} \\
Invited speaker on an application-driven subsampling algorithm, with emphasis on theoretical motivation,
practical implementation, and performance in large-scale statistical modelling.

\section*{Technical Skills}
\begin{itemize}
\item Programming: Python, R, MATLAB
\item Statistics: mathematical statistics, data modelling, applied statistics
\item Machine Learning \& AI: proficient use of large language models (LLMs); in-depth understanding of machine learning and big data algorithms, including core principles and recent advances
\item Tools: Microsoft Excel, Microsoft Office
\end{itemize}

\section*{Languages}
English (Fluent), Mandarin Chinese (Native)

\end{document}